---
title: "Importance Of Gender Roles and Child Marriage In Turkey"
author: 
  - Kul, Sılanur Ayşen[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
    Child marriages are one of the most significant causes of gender inequality within families in Turkey, as well as a widespread social problem observed worldwide. This situation necessitates a comprehensive examination of child marriages to understand and address all aspects of this issue. The findings of this study highlight that child marriages are a significant consequence of gender inequalities observed in social, political, and economic spheres. Moreover, it reveals that child marriages perpetuate gender inequality in the lives of women. This study aims to shed light on the significant socio-cultural aspects of child mothers and child marriages in Turkey, focusing on regional variations. 
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: 19080406, [Github Repo](https://github.com/silakul/19080406.FINAL)


# Introduction
Child marriage, also known as adolescent marriage, early marriage, forced marriage, and child brides, generally refers to the practice of children, particularly girls, under the age of 18 getting married. It is a pervasive issue that transcends cultural boundaries and is not confined to any specific culture or region. Children under the age of 18 who are married are considered a vulnerable group worldwide [@paul2019effects]. Consequently, this subject necessitates academic scrutiny and comprehensive analysis.

Child marriage in Turkey is an under-researched topic that requires further investigation and analysis. There is a need for comprehensive studies examining the current situation of child marriage from medical, social, economic, and legal perspectives. Such research is crucial for gaining a deeper understanding of the issue and developing effective strategies to address child marriage in Turkey. By exploring the various dimensions of child marriage, policymakers, organizations, and communities can make informed decisions and take appropriate actions to protect children's rights and promote gender equality.

Based on the extensive literature and real-life examples, it becomes evident that family and marriage are primary institutions where gender dominance prevails. Within this context, social events entwined with power dynamics shaped by gender roles occur both prior to making the decision to marry, during the marriage, and even after marriages have ended [@duman2019ccocuk]. Child marriage, the focus of this study, emerges as both a cause and a consequence of these events. This particular form of marriage, which will be explored in relation to the societal expectations imposed on women and men, arises from various reasons and has diverse impacts on social life.

When examining the causes and effects, similar patterns are observed worldwide, including in Turkey. As evidenced by the statistical information presented in the subsequent sections of this study, although there is a decreasing trend in early marriages, it remains a pressing social problem that inflicts deep wounds and imposes severe restrictions, particularly on the lives of girls.




## Literature Review

The distribution of child marriages in Turkey reveals a declining trend in their numbers over the years, alongside regional variations in the average age at marriage. 


# Data


Based on data published by TUIK in 2022, girl child marriages have decreased according to official statistics. The percentage of child brides in the 16-17 age group decreased from 5.2% in 2015 to 4.6% in 2016. When examining the provincial data, Ağrı province has the highest rate of marriages involving girls under 18, with a rate of 15.7%. Conversely, Tunceli province has the lowest rate at 1.1%. These findings highlight the need for targeted efforts to address child marriages and implement measures that protect the rights of underage girls across different regions in Turkey [@kiran2017toplumsal]. The likelihood of giving birth to a first child shows an upward trend with age: 0.4% at 15, 2.2% at 16, 4.4% at 17, 9.7% at 18, and 12.9% at 19. So, as age increases, the chances of becoming a mother for the first time also increase. In Turkey, the proportion of adolescent childbearing is 35% [@oren2019investigation].



```{r}
library(tidyverse)
library(here)
survey <- read_csv(here("data/survey.csv"))
```

Note that code options are edited in some of the code chunks in the Rmd file.

```{r, echo=FALSE}
library(xtable) 
library(summarytools)
st_options(lang = "en")
```

With the `echo=FALSE` option, prevent the codes from appearing in the derived pdf file and report your results in tables.

```{r results='asis', echo=FALSE}
survey %>%
  select("sex", "credits", "handedness", "height", "handspan") %>% 
  descr(stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE) %>% 
  xtable(caption = "Summary Statistics",
         label = "tab:summary",
         align = c("l", "c", "c", "c", "c", "c")) %>% 
  print(booktabs = TRUE, comment = FALSE, caption.placement = "top")
```


# Methods and Data Analysis
.

For example, if you are performing regression analysis, discuss your predicted equation in this section. Write your equations and mathematical expressions using $LaTeX$.

$$
Y_t = \beta_0 + \beta_N N_t + \beta_P P_t + \beta_I I_t + \varepsilon_t
$$

This section should also include different tables and plots. You can add histograms, scatter plots (such as Figure \@ref(fig:plot)), box plots, etc. Make the necessary references to your figures as shown in the previous sentence.


```{r plot, fig.align='center', fig.cap='An Awesome Plot'}
survey %>% 
  ggplot(aes(x = handedness, y = handspan)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous("Handedness") + 
  scale_y_continuous("Handspan")
```


# Conclusion
Summarize the results of your analysis in this section. Discuss to what extent your results responded to the research question you identified at the beginning and how this work could be improved in the future.

**References section is created automatically by Rmarkdown. There is no need to change the references section in the draft file.**

**_You shouldn't delete the last 3 lines. Those lines are required for References section._**

\newpage
# References {#references}
<div id="refs"></div>

